E-jection fraction - Tracking how your website pumps out E-Mails

### 2016-05-13 Background/lang_aff.tex
prelim edit chap2

\begin{itemize}
\item{\textbf{PHP}} - PHP was one of the first languages found to have this vulnerability in its implementation of the \texttt{mail()} function. The early finding of this vulnerability can be attributed in part to the success and popularity of the language for creating web pages. According to w3techs \cite{W3techs}, PHP is used by 81.9\% of all the websites in existence, thereby creating the possibility of this vulnerability to be widespread.

>>>>

\begin{itemize}
\item{\textbf{PHP}} - PHP was one of the first languages found to have this vulnerability in its implementation of the \texttt{mail()} function at the time of release of PHP~4.0. The early finding of this vulnerability can be attributed in part to the success and popularity of the language for creating web pages. According to w3techs \cite{W3techs}, PHP is used by 81.9\% of all the websites in existence, thereby creating the possibility of this vulnerability to be widespread.
